---
title: "p8105_hw5_ww2579"
author: "Wenzhao Wu"
date: "11/10/2020"
output: github_document
---

```{r setup}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 12,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Read in the data. 

```{r}
homicide_df = 
  read_csv("./homicide_data.csv") %>%
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved")
  ) %>%
  select(city_state, resolved)
```

Let's look at this a bit

```{r}
aggregate_df = homicide_df %>%
  group_by(city_state) %>%
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved),
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull (hom_total)) %>%
  broom::tidy()
```

Try to iterate

```{r}
results_df = 
  aggregate_df %>%
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)), 
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
 ) %>%
  select(-prop_tests) %>%
  unnest(tidy_tests) %>%
  select(city_state, estimate, conf.low, conf.high)
```

## Problem 2

Tidy and iterate over all csv files

```{r}
tidy = function(y) {
  pivot_longer(
    data = y,
    week_1:week_8,
    names_to = "week",
    values_to = "value",
    names_prefix = "week_") %>%
  mutate(
    week = as.factor(week))
}

path_df = 
  tibble(path = list.files("./lda_data")) %>%
  mutate(path = str_c("lda_data/", path),
         data = map(.x = path, ~read_csv(.x)),
         tidied = map(.x = data, ~tidy(.x)),
         path = str_replace(path, "lda_data/exp_", "exp "),
         path = str_replace(path, "lda_data/con_", "con "),
         path = str_replace(path, ".csv",""))

```

Make a spaghetti plot showing observations on each subject over time.

```{r}
unnesting = 
  path_df %>%
  unnest(tidied)

plot = unnesting %>%
  ggplot(aes(x = week, y = value, color = path, group = path)) +
  geom_point() +
  geom_line() +
  labs(title = "Con vs Exp over 8 weeks") +
  ggsave("spaghetti_plot.pdf")
  
```

Comments: The graph above shows observations of each subject (10 for control group, 10 for experimental group) over 8 weeks. It could be observed that in general, subjects from the experimental group have larger values of observation, compared to those from the control group. 


## Problem 3

t.test with one dataset

```{r}
set.seed(1)
samp = rnorm(30,1,5)
t.test(samp) %>%
  broom::tidy()
```

t.test with 5000 datasets for different mu's 

```{r}
n = 30
mu = 0
sigma = 5
set.seed(1)


sim = function(n = 30, mu, sigma = 5) {
  samp = tibble(
    x = rnorm(n, mean = mu, sd = sigma))
  samp %>%
    t.test(conf.level = 0.95, formula = samp~1) %>%
    broom::tidy()}

sim_results = tibble(diff_mu = c(0,1,2,3,4,5,6)) %>%
  mutate(output = 
           map(.x = diff_mu, ~rerun(5000, sim(mu = .x))))
```

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis

```{r}
t_test = unnest(unnest(sim_results)) %>%
  mutate(diff_mu = as.factor(diff_mu))
power_plot = 
  t_test %>%
  filter(p.value < 0.05) %>%
  group_by(diff_mu) %>%
  summarise(n_power = n()) %>%
  mutate(prop_power = n_power/5000) %>%
  ggplot(aes(x = diff_mu, y = prop_power, fill = diff_mu)) +
  geom_col() +
  theme(legend.position = "none") +
  labs(title = "Power of Test",
       x = "True mu",
       y = "Proportion of Rejecting the Null") +
  ggsave("power_plot.pdf")
  
```

Describe the association between effect size and power.


Make a plot showing the average estimate of μ^ on the y axis and the true value of μ on the x axis.

```{r}

```

